---
title: "**Code Overview**"
subtitle: "_KuskoHarvEst Documentation_"
date: '`r paste0("Last Updated: ", KuskoHarvEst:::basic_date(lubridate::today()))`'
author: "`r d = readLines('../../../../../../DESCRIPTION'); paste0('Package ', d[3])`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

_This document provides an overview of the coding framework used by 'KuskoHarvEst' which enables it to do its job. It is intended for users wishing to understand how the code works._

**Most users will not need to review this document**. It is intended for users who are interested in learning how the code works and the roles that each of the many functions play. 

'KuskoHarvEst' does three main things:

1. **Performs estimation** of effort and harvest resulting from one calendar day of fishing in which flights were conducted to count fishing trips and surveys were conducted to sample the harvest.
2. **Produces PDF reports** that document the results of the estimation.
3. **Provides interactivity** to perform these tasks without having to edit a single line of code.

Each of these tasks is supported by many functions that have been written for custom use. This document contains a [catalog of all functions](#catalog) that briefly describes its purpose and functionality as well as a [brief tutorial](#tutorial) for how to produce an estimate without using the interactive functionality and using only R code.

# Tutorial for Non-Interactive Estimation {#tutorial}

At some point someone might wish to create a harvest estimate without using the interactive workflow. An example would be to reanalyze the data from many previous fishing opportunities. Writing code could save a lot of time relative to manually producing each estimate with the interactive workflow. This section provides an example for how to produce an estimate with only code.

Before beginning, ensure the package is loaded:

```{r}
library(KuskoHarvEst)
```

## Step 0: Prepare the Data Files

`KuskoHarvEst` includes the data from the June 12, 2020 fishing opportunity which will be used here as an example. Extract the file paths/names of these files:

```{r}
data_files = list.files(KuskoHarvEst:::resource_path("05-example-data"), full.names = TRUE)
```

Note that three files store interview data and one stores flight counts. 

```{r}
basename(data_files)
```

Determine which files are used for which purpose:

```{r}
flight_file = data_files[stringr::str_detect(data_files, "Flight_counts")]
interview_files = data_files[!stringr::str_detect(data_files, "Flight_counts")]
```

Ensuring the data files are properly formatted is a key step to using 'KuskoHarvEst' successfully. Full instructions can be found `r KuskoHarvEst:::link_to_doc("01-raw-data.html")`.

## Step 1: Define Global Options

This code sets some options that will be used by some of the background functions used in the package. Do not change them unless you have a good reason to:

```{r}
options(
  soak_sd_cut = 3,
  net_length_cut = 350,
  catch_per_trip_cut = 0.05,
  central_fn = mean,
  pooling_threshold = 10
)
```

## Step 2: Prepare Flight Data

Assuming the data file is formatted properly, preparing the flight data is simple:

```{r}
flight_data = prepare_flights(flight_file)
```

This object contains the same information as contained in the raw data file, only now in a standardized format:

```{r, echo = FALSE}
flight_data
```

Each row is a flight and the columns store the flight times and the counts by gear type and stratum.

## Step 3: Prepare Interview Data

Again, assuming the data files are formatted properly, preparing the interview data is also simple:

```{r}
interview_data = prepare_interviews(interview_files)
```

Oftentimes some warnings will result from this step. These warnings notify you that some aspects of the data file(s) may not be ideal how the program has treated them. See `r KuskoHarvEst:::link_to_doc("03-interview-flight-data-tool.html", "this document")` for how to interpret the messages that may be returned by this function.

The output object stores interviews as rows and variables as columns just as in the raw data files, but again, it is now in a standardized and combined format. Here are the first 20 rows:

```{r, echo = FALSE}
head(interview_data, 20)
```

The columns that start with `"suit_"` store a `TRUE` if that object is suitable for a purpose and `FALSE` if not and the `"note"` column stores some information about records that required special treatment.

## Step 4: Produce Effort Estimates

Next, produce effort estimates using `estimate_effort()`. June 12, 2020 was a opportunity that allowed both set and drift net harvest, so estimates must be made for two gear types separately:

```{r}
# estimate drift net effort
drift_effort_info = estimate_effort(interview_data, flight_data, gear = "drift", method = "dbl_exp")

# estimate set net effort
set_effort_info = estimate_effort(interview_data, flight_data, gear = "set", method = "max_per_stratum")
```

The `method` argument defines the estimator type:

* `method = "dbl_exp"` performs corrections for double counted trips (on consecutive flights) and expansions for trips that were likely to have occurred during times no flights occurred and is used for drift net effort.
* `method = "max_per_stratum"` calculates effort as the sum of the maximum strata-specific counts and is used for set net effort.

The total effort estimate is stored here:

```{r}
drift_effort_info$effort_est_total
```

and the effort estimate for each stratum is stored here:

```{r}
drift_effort_info$effort_est_stratum
```

For the drift estimate, other useful information is contained in this object:

* `drift_effort_info$trip_counts`: contains how many interviews were from trips available to be counted on each flight (`f1` and `f2`), how many interviewed trips were available to be counted on any flight (`yes_counted`) or no flights (`not_counted`), and how many interviewed trips were available to be counted by multiple flights (`f1&f2`): 

    ```{r, echo = FALSE}
    drift_effort_info$trip_counts
    ```

* `drift_effort_info$p_T1_given_T2`: contains the proportion of interviewed trips available to be counted on a subsequent flight that were also available to be counted on the previous flight:

    ```{r, echo = FALSE}
    drift_effort_info$p_T1_given_T2
    ```

* `drift_effort_info$effort_count`: contains the effort estimate that accounts for all trips that occurred during times they could have been counted by any flight:

    ```{r, echo = FALSE}
    drift_effort_info$effort_count
    ```

* `drift_effort_info$effort_not_count`: contains the effort estimate for trips that occurred during times they could not have been counted by any flight:

    ```{r, echo = FALSE}
    drift_effort_info$effort_not_count
    ```

* `drift_effort_info$effort_per_interview`: contains the expansion factor for estimating `drift_effort_info$effort_not_count`

    ```{r, echo = FALSE}
    drift_effort_info$effort_per_interview
    ```

In practice, most users will not need to access these elements and need only concern themselves with `drift_effort_info$effort_est_total`.

## Step 5: Produce Harvest Estimate (with bootstrap)

Next, produce harvest estimates using a non-parametric bootstrap using `bootstrap_harvest()`. Estimates must be generated for each gear type separately, but this function performs estimates for all species and geographic strata all at once. Note that the argument `n_boot` is required: this is the number of bootstrap samples to generate; 100 is used here for demonstration but for real applications this should be set to 1000.

```{r}
# estimate (via bootstrap) drift net harvest for all species and and strata
boot_out_drift = bootstrap_harvest(interview_data, effort_info = drift_effort_info,
                                   gear = "drift", n_boot = 100, stratify_interviews = TRUE)

# estimate (via bootstrap) set net harvest for all species and and strata
boot_out_set = bootstrap_harvest(interview_data, effort_info = set_effort_info,
                                 gear = "set", n_boot = 100, stratify_interviews = FALSE)
```

The output of these objects looks like this (first 20 rows of `boot_out_drift`):

```{r, echo = FALSE}
head(boot_out_drift, 20)
```

Notice that it includes an identifier for bootstrap iteration (`iter`), the date the estimate applies to (`date`), the gear the estimate applies to (`gear`), the geographic stratum (`stratum`, including a "total" category), and estimates for each salmon species as well as the total across species. Estimates have been rounded to the nearest whole fish.

These two objects must be combined into one object that stores all output as well as a total across gears:

```{r}
# sum up across gears
boot_out_total = data.frame(iter = boot_out_drift$iter, 
                            date = boot_out_drift$date,
                            gear = "total", 
                            stratum = boot_out_drift$stratum,
                            chinook = rowSums(cbind(boot_out_drift[,"chinook"], boot_out_set[,"chinook"]), na.rm = TRUE),
                            chum = rowSums(cbind(boot_out_drift[,"chum"], boot_out_set[,"chum"]), na.rm = TRUE),
                            sockeye = rowSums(cbind(boot_out_drift[,"sockeye"], boot_out_set[,"sockeye"]), na.rm = TRUE),
                            total = rowSums(cbind(boot_out_drift[,"total"], boot_out_set[,"total"]), na.rm = TRUE)
)

# combine drift, set, and total into one data frame of bootstrap output
boot_out = rbind(boot_out_total, boot_out_drift, boot_out_set)
```

## Step 6: Summarize Output

The final step is to summarize the bootstrap output; this is the role of the `report()` function. Using it without any arguments will summarize `boot_out` for the total harvest (across strata, species, and gears):

```{r}
report()
```

If numerical rather than character output is required, use the `return_numeric` argument

```{r}
report(return_numeric = TRUE)
```

If confidence intervals are not desired, use the `CI` argument

```{r}
report(return_numeric = TRUE, CI = FALSE)
```

To get total harvest by all gears and strata for Chinook salmon:

```{r}
report(spp = "chinook")
```

To get Chinook salmon harvest by drift nets in stratum A:

```{r}
report(spp = "chinook", gear = "drift", stratum = "A")
```

To get chum salmon harvest by all gears in each stratum:

```{r}
sapply(unique(boot_out$stratum), function(stratum) report(spp = "chum", stratum = stratum))
```

By default, `report()` will use an object called `boot_out` to calculate these summaries. If you have another object to summarize that is not called `boot_out`, pass it to the `boot_out_use` argument.

# 'KuskoHarvEst' Function Catalog {#catalog}

There are many functions contained in 'KuskoHarvEst' that enable it to do its job. These functions can be broken into six main types:

1. **Data Processing** functions take the raw input files and convert them to a standardized format ready to be used by the rest of the functions. Also performs quality assurance checks to verify that unreliable or unsuitable records are not used.
2. **Core Estimation** functions perform the effort and harvest estimation, including bootstrapping.
3. **Output Element** functions take the results of estimation/data preparation functions and produces output to be displayed somewhere (e.g., summarize results, place summaries in tables, create figures, etc.)
4. **Rmarkdown** functions automate creating a YAML header and `.Rmd` source file to be knitted that contains all of the code needed to produce an estimate and build a PDF report.
5. **Interactive Tool** functions prevent the user from needing to know how to write or read R code by wrapping all steps in interactive RStudio add-ins.
6. **Miscellaneous Helper** functions contain miscellaneous code that must be called in different places to help the other functions do their jobs. Many of these functions take input in one format and change it to another. Although the role they serve is important, most users will not need to become familiar with them.

If you ever peruse the source code (found [here](https://github.com/bstaton1/KuskoHarvEst), in the "R" subdirectory), you will find that the files are organized according to these types by the prefix `01-data-*.R` for data processing functions, `02-est-*.R` for core estimation functions, etc.

Users should note that the vast majority of these functions operate "in the background" and will never need to be called directly. The principle functions used by the user are described above in the [tutorial](#tutorial) and include:

* `prepare_flights()` and `prepare_interviews()`
* `estimate_effort()`
* `bootstrap_harvest()`
* `report()`

This catalog is intended for users wishing to gain a more complete understanding of how the interworkings of the package function. More details about any of these functions, including what arguments they accept can be accessed using `?KuskoHarvEst::fName` where `"fname"` is replaced by the name of the function of interest.

## Data Processing Functions

* `prepare_flights()` takes a file path to the raw flight count data file and standardizes it for use by other functions.
* `prepare_interviews_one()` takes a file path to the interview data collected by one monitoring organization and standardizes it for use by other functions.
* `prepare_interviews()` a wrapper around `prepare_interviews_one()` to prepare all interview data source files. Also performs quality assurance/usability checks for each interview.
* `suitable_for()` checks each interview for its suitability to be used for a purpose. Purposes include things like: effort estimation (must have trip times recorded), the presence of all catch rate data, the reliability of all catch rate data, etc. Is a wrapper around the many small quality assurance checks listed below.
* A whole host of small quality assurance checks, some of which are self-explanatory. These functions all take the output of `prepare_interviews_one()` and return a logical vector, one element for each interview.
  * `has_gear()`
  * `has_trip_times()`
  * `has_net_length()`
  * `has_soak()`
  * `is_possible_trip()` -- a trip is considered impossible if the trip end time is before the trip start time
  * `is_possible_soak()` -- a soak time is considered impossible if the soak duration is recorded to be longer than the trip duration
  * `is_complete_trip()` -- in some years law enforcement has conducted rolling creel interviews and the fisher trips were incomplete at the time of the survey. This means some of the data cannot be used for all purposes and that they need special care. Checks if the data source is `"LE"`
  * `is_normal_net()` -- returns a `FALSE` if the net length exceeds some length defined by the user, which defaults to 350 feet.
  * `is_soak_outlier()` -- checks each soak time for consistency with other soak times for that gear type. If the soak time is >X SDs away from the mean of all other soak times for that gear type, it will be flagged as a soak time outlier. The value of X is selected by the user and defaults to 3.
  * `is_short_incomplete_soak()` -- if the trip is incomplete and shorter than the shortest completed trip, this function will return a flag indicating its catch rate data should not be used.
  * `is_catch_per_trip_outlier()` -- if leaving out an interview changes the estimate of mean catch/per trip by greater than X%, it is flagged as an outlier and its catch rate data will not be used in the average. Only done for drift trips.
  * `unique_start_dates()` -- extracts the unique start dates for all interviews. All code in this package assumes it is working on one day at a time.
  * `check_options()` -- this package requires that some global options are defined. This function checks that all required options have been set. The options are: `"soak_sd_cut"` (passed to `is_soak_outlier()`), `"net_length_cut"` (passed to `is_normal_net()`), `"catch_per_trip_cut"` (passed to `is_catch_per_trip_outlier()`), `"central_fn"` (passed to `estimate_catch_per_trip()`), and `"pooling_threshold"` (passed to `get_use_strata()`).
* `randomize_data()` resamples with replacement from a set of interviews; used to support the non-parametric bootstrap.

## Core Estimation Functions

* `estimate_effort()` -- performs the calculations for estimating effort for either drift nets or set nets
* `stratify_effort()` -- apportions the aggregate effort estimate into strata-specific estimates
* `estimate_harvest()` -- estimates harvest by species and geographic stratum as `effort * catch_per_trip`
* `bootstrap_harvest()` -- replicates resampling with replacement from interview data and calling `estimate_harvest()` on each resample to generate a distribution of plausible harvest estimates
* `estimate_catch_per_trip()` -- performs the calculations for estimating catch per fisher trip (by gear and stratum) using only those records that are suitable for each component in the calculation
* `get_use_strata()` -- determines the pooling strategy to use for interview data when some strata are particularly data-poor

## Output Element Functions

* `report()` -- summarizes the output of `bootstrap_harvest()`; see the [code tutorial](#tutorial) step 6 for usage examples
* `make_histogram()` -- generates one histogram showing the distribution of a quantity across interviewed trips
* `make_histograms()` -- wrapper for `make_histogram()` that generates a multi-panel plot of six histograms
* `make_histogram_caption()` -- the caption of the histogram depends on the data sources available; this function automates this
* A handful of functions dedicated to making a specific kind of table for displaying in PDF reports:
  * `make_interview_data_table()`
  * `make_flight_data_table()`
  * `make_strata_summary_table()`
  * `make_johnson_summary_table()`
  * `make_goals_summary_table()`
  * `make_appendix_table()`
  * `make_effort_sensitivity_table()`
  * `make_harvest_sensitivity_table()`
* `make_effort_plot()` -- generates a diagnostic plot that shows the interviewed trips and flight times as an overlay; a visual for examining correct entry of time information and seeing how many trips were available to be counted on each flight.
* Three functions that create the sensitivity analysis scenarios: combinations of flight and interview data exclusion. These are: `create_flight_combos()`, `create_interview_combos()`, and `create_harvest_combos()`

## Rmarkdown Functions

See the section on [construcing Rmarkdown source scripts](#Rmd) for details on what these functions do. Essentially, they enable automating construction of the source code that generates the PDF reports.

* `build_yaml()`
* `build_estimate_report_Rmd()`
* `build_sensitivity_report_Rmd()`
* `pdf_report()`

## Interactive Tool Functions

* `meta_tool()` -- source code to execute the interactive tool for entering the opportunity meta-data.
* `data_tool()` -- source code to execute the interactive tool for processing and exploring interview and flight data.
* `rmd_tool()` -- source code to execute the interactive tool for selecting among output elements to include in the PDF reports, constructing the Rmd scripts, and building the PDF output files.
* `help_tool()` -- source code to execute the interactive tool for accessing documentation and more information.

## Miscellaneous Helper Functions

* `resource_path()` -- returns the path to a file or directory in the user's 'KuskoHarvEst' installed package within the path `.../library/KuskoHarvEst/rstudio/templates/project/resources/`. This location stores many important files that need to be easily accessed. 
* `KuskoHarvEst_skeleton()` -- builds a blank project from a template that is suitable for 'KuskoHarvEst' usage
* `percentize()` -- converts a number (e.g., `0.105`) to a percent suitable for printing in documents (e.g., `"10.5%"`)
* `tinyCI()` -- adds LaTeX code to the output of `report()` to format the confidence intervals smaller than the mean text
* `capitalize()` -- captializes the first letter of a character string
* `combine_datetime()` -- combines a date (stored as M/D/YYYY) and time (stored as H:MM) into a standardized date time object that can be used by any 'lubridate' function; provides standardized treatment of dates and times
* `file_date()` -- converts a datetime object into a format suitable to serve in a file name 
* `basic_date()` -- converts a datetime object into a more human-readable format
* `short_datetime()` -- converts a datetime object into a more human-readable format
* `add_vspace()` -- enables changing how much space is placed at the bottom of a LaTeX table generated by a `knitr::kable() %>% kableExtra::fun()` tool chain.
* `link_to_doc()` -- creates a Rmarkdown hyperlink to a 'KuskoHarvEst' documentation file -- for embedding these links within other documentation files so they can be easily cross referenced.

# Other R Objects

'KuskoHarvEst' includes two objects that contain information that is useful when building output. 

* An object named `source_names` that includes information about what each of the data source codes mean. **If new data sources are collected in the future, this object needs to be updated.**

    ```{r}
    KuskoHarvEst:::source_names
    ```

* An object names `strata_names` that includes information about what each of the stratum codes mean. **If new boundaries of the strata are defined, or if new strata are to be included, this object needs to be updated.**

    ```{r}
    KuskoHarvEst:::strata_names
    ```

# Construction of Rmarkdown Source Scripts {#rmd}

The PDF report is generated by code that runs the analysis and embeds the results in the output at the same time using a framework called Rmarkdown. The file that contains the code is called an Rmarkdown (Rmd) source script. However, the code contained in this script depends on some characteristics of the opportunity and data available such as:

* How many flights were flown
* If the opportunity was set net only, or allowed both set nets and drift nets to be used
* If a set net estimate is desired or not
* Which output tables are desired

In previous versions of this code, the user had to copy the Rmd script from the previous estimate and edit it by hand to reflect the features of the new estimate. In 'KuskoHarvEst', all of the possibilities for different code that could go in the Rmd script has now been placed into many separate files that then are combined as needed to build the final Rmd source script that ultimately becomes rendered. This is the purpose of `build_estimate_report_Rmd()` and `build_sensitivity_report_Rmd()` -- they accept options for which features should be included and they combine the separate files. The function `build_yaml()` builds what is called a YAML header for the Rmd script, which contains some basic instructions for how to convert the code to a PDF.

The location on your computer that houses the many separate files containing the Rmd code components that ultimately become combined can be found using this code:

* Code that is used across multiple outputs:

    ```{r, eval = FALSE}
    KuskoHarvEst:::resource_path("01-common")
    ```

* Code that is used only by the estimate report:

    ```{r, eval = FALSE}
    KuskoHarvEst:::resource_path("02-estimate-report")
    ```

* Code that is used only by the sensitivity report:

    ```{r, eval = FALSE}
    KuskoHarvEst:::resource_path("03-sensitivity-report")
    ```

Rmarkdown includes default configurations for the PDF output (e.g., font, margins, overall spacing, title format, page numbering, footer contents, etc.). These features have been edited using a Pandoc/LaTeX template file found at the path returned by `KuskoHarvEst:::resource_path("01-common/report_template.tex")`. Further, instead of using the default output class of `rmarkdown::pdf_document()`, 'KuskoHarvEst' includes `KuskoHarvEst:::pdf_report()` which uses this template automatically.


