---
title: Improving the Kuskokwim In-Season Salmon Harvest Estimation Workflow
subtitle: Project Summary Report
bibliography: cites.bib
bib-style: "`r msdown::msdown_resources('0-templates/myapalike.bst')`"
cite-author-year-sep: ""
csl: "`r msdown::msdown_resources('0-templates/citation-style.csl')`"
link-citations: false
body-on-new-page: false
watermark: false
fontsize: 12pt
fontfamily: mathpazo
geometry: margin=1in
singlespace: true
lineno-title-page: false
lineno-main-text: false
lineno-bib: false
lineno-figs-tabs: false
ragged: false
theprefix: ""
caption-by-figure: true
caption-by-table: true
listoffigures: false
listoftables: false
citecolor: black
linkcolor: black
urlcolor: cyan
site: bookdown::bookdown_site
header-includes:
  - \usepackage{fontawesome}
  - \captionsetup[figure]{font=small}
---

```{r, include = F}
# load in packages
library(knitr)
library(kableExtra)
library(msdown)

# clear the workspace
rm(list = ls())

# set global RMarkdown chunk options: never print code, output, or warnings/messages
if (is_latex_output()) {
  knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.align = "center")
} else {
  knitr::opts_chunk$set(echo = F, message = F, warning = F)
}
```

```{r word-authors, eval = !is_latex_output()}
yaml = rmarkdown::yaml_front_matter("index.Rmd")
author_list = yaml$author
authors = unlist(lapply(author_list, function(a) a$name))
```

`r if (!is_latex_output()) paste(authors, collapse = ", ")`

`r if (!is_latex_output()) "**NOTE**^[The source code for our manuscript is rendered here as a word document. As a result, some of the formatting is not nearly as clean as the PDF output. Please disregard the formatting in this copy; it was provided so you can use 'track-changes' when providing feedback (_please do so, as this will allow me to easily find your changes and incorporate them in the next draft_). If you have concerns about the formatting, please consult the PDF output to see how it will look when sent to the journal - or request it from me if I didn't send it along with this copy.]"`
