
\clearpage
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{A\arabic{figure}}
\renewcommand\thetable{A\arabic{table}}

# Appendix A: Detailed Interview Summaries {-}

**Column Meanings**

* **Area**: the area of the river the trip occurred in
* **N**: the number of interviews with usable information in each area
* **Min**: the minimum value among trips in each area
* **25%**: the value that 25% of trips fell below in each area
* **Mean**: the average value across trips in each area
* **75%**: the value that 75% of trips fell below in each area
* **Max**: the maximum value among trips in each area

_Information is for drift net trips only._

```{r chinook-appendix-table}
make_appendix_table(interview_data, "drift", "chinook")
```

```{r chinook-rate-appendix-table}
make_appendix_table(interview_data, "drift", "chinook_rate")
```

```{r chum-appendix-table, eval = split_chum_sockeye}
make_appendix_table(interview_data, "drift", "chum")
```

```{r chum-rate-appendix-table, eval = split_chum_sockeye}
make_appendix_table(interview_data, "drift", "chum_rate")
```

```{r sockeye-appendix-table, eval = split_chum_sockeye}
make_appendix_table(interview_data, "drift", "sockeye")
```

```{r sockeye-rate-appendix-table, eval = split_chum_sockeye}
make_appendix_table(interview_data, "drift", "sockeye_rate")
```

```{r chum-sockeye-appendix-table, eval = !split_chum_sockeye}
make_appendix_table(interview_data, "drift", "chum+sockeye")
```

```{r chum-sockeye-rate-appendix-table, eval = !split_chum_sockeye}
make_appendix_table(interview_data, "drift", "chum+sockeye_rate")
```

```{r p-chinook-appendix-table}
make_appendix_table(interview_data, "drift", "p_chinook")
```

```{r soak-duration-appendix-table}
make_appendix_table(interview_data, "drift", "soak_duration")
```

```{r trip-duration-appendix-table}
make_appendix_table(interview_data, "drift", "trip_duration")
```
