
```{r}
appendix_counter = appendix_counter + 1
```

\clearpage
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{`r LETTERS[appendix_counter]`\arabic{figure}}
\renewcommand\thetable{`r LETTERS[appendix_counter]`\arabic{table}}

```{r}
appendix_gear = "drift"
```

# Appendix `r LETTERS[appendix_counter]`: Detailed Interview Summaries {-}

**Column Meanings**

* **Area**: the area of the river the trip occurred in
* **N**: the number of interviews with usable information in each area
* **Min**: the minimum value among trips in each area
* **25%**: the value that 25% of trips fell below in each area
* **Mean**: the average value across trips in each area
* **75%**: the value that 75% of trips fell below in each area
* **Max**: the maximum value among trips in each area

_Information is for `r appendix_gear` net trips only._

```{r appendix-tables, results = "asis"}
make_appendix_tables(
  interview_data = interview_data,
  gear = appendix_gear,
  include_rates = TRUE,
  split_chum_sockeye = params$split_chum_sockeye,
  extra = c("trip_duration", "soak_duration"),
  nonsalmon = FALSE
  )
```
