\clearpage
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{NONSALMON_APPENDIX_REPLACE\arabic{figure}}
\renewcommand\thetable{NONSALMON_APPENDIX_REPLACE\arabic{table}}

# Appendix NONSALMON_APPENDIX_REPLACE: Non-salmon Harvest Information {-}

```{r estimate-harvest-nonsalmon}
# estimate (via bootstrap) drift net harvest for all species and and strata
boot_out_drift = bootstrap_harvest(interview_data, drift_effort_info,
                                   gear = "drift", n_boot = n_boot, stratify_interviews = TRUE, nonsalmon = TRUE)

# don't perform a set net estimate

# combine drift, set, and total into one data frame of bootstrap output
boot_out <<- combine_boot_out(boot_out_drift = boot_out_drift, boot_out_set = NULL)
```

* An estimated total of **`r report()`** non-salmon (sheefish and whitefishes) were harvested.
  * An estimated total of **`r report(spp = "sheefish")`** sheefish were harvested.
  * An estimated total of **`r report(spp = "whitefish")`** whitefishes were harvested.

```{r}
make_strata_summary_table(interview_data, "drift", nonsalmon = TRUE)
```

```{r}
make_appendix_table(interview_data, "drift", "sheefish")
```

```{r}
make_appendix_table(interview_data, "drift", "whitefish")
```
