
# Effort Sensitivity Analyses {-}

::: {.small data-latex=""}
_In the tables below, "Pr(F1|F2)" is the probability that a trip counted on flight 2 was also counted on flight 1 (the estimator corrects for double-counting; this column will not display if only one flight was made). "Trips per interview" is an estimate of how many actual trips occurred per interview that was conducted, and is used to expand the effort estimate for interviews that are known to have occurred but could not have been counted because they started and stopped during times when the flights were inactive. "Trips not observed" is the estimated number of trips that fall in this expanded category._
:::

## Exclusion of Flight Data {-}

::: {.small data-latex=""}
_This analysis leaves out all combinations of flight data and re-calculates the drift net effort estimates. This helps give a sense of how the estimate would have been different had fewer flights been conducted. Generally, you want to see small changes because with good interview data coverage, the effort estimator should be robust to fewer flights. If there are large changes (e.g., >50%), that indicates that the distribution of fishing effort indicated by the interview data and the flight data are inconsistent, and emphasizes that conducting several flights within an opportunity is important to obtain a good estimate._
:::

```{r perform-flight-data-exclusion}
# create combinations of flights to retain or discard
flight_combos = KuskoHarvEst:::make_flight_combos(flight_data)

# apply the effort estimator to each combination
flight_effort_scenarios = lapply(1:nrow(flight_combos), function(i) {
  estimate_effort(interview_data, flight_data[unlist(flight_combos[i,]),], gear = "drift", method = "dbl_exp")
})

# build the output table
KuskoHarvEst:::effort_sensitivity_table(flight_effort_scenarios, flight_data, flight_combos)
```

\clearpage

::: {.small data-latex=""}
_These plots display the times that the trip from each used interview was active and able to be counted via aerial count (vertical lines). Solid black lines indicate the trip would have been counted once, dashed lines indicate the trip would have been counted twice, and dotted lines indicate the trip would have been counted three times. Blue solid lines are trips that could not have been counted. Horizontal grey regions indicate the times the flights were active._
:::

```{r make-plots-flight-data-exclusion, results = "asis", fig.height = 4, fig.width = 7}
junk = lapply(1:nrow(flight_combos), function(i) {
  cat("### Flight(s)", paste(which(unlist(flight_combos[i,])), collapse = " & "), "{-}")
  junk = effort_plot(flight_data[unlist(flight_combos[i,]),], flight_effort_scenarios[[i]], FALSE)
})
```

## Exclusion of Interview Data {-}

:::{.small data-latex=""}
_This analysis leaves out all combinations of interview data sources and re-calculates the drift net effort estimates (the scenario column indicates which data sources were kept). This helps give a sense of how much each data source affects the overall estimate, and how much the estimate would have been different had fewer data sources been available. Generally, you want to see relatively small changes when leaving out data -- this is an indication that each source took a random sample of the fishers it could have sampled with respect to trip times. If large changes occur (e.g., >50%), that is not necessarily a problem, but it is good information to know._
:::

```{r perform-interview-data-exclusion}
# create combinations of interview data sources to retain or discard
interview_combos = KuskoHarvEst:::make_interview_combos(interview_data)

# apply the effort estimator to each combination
interview_effort_scenarios = lapply(1:nrow(interview_combos), function(i) {
  combos_use = unlist(interview_combos[i,])
  estimate_effort(interview_data[interview_data$source %in% names(combos_use)[which(combos_use)],], flight_data, gear = "drift", method = "dbl_exp")
})

# build the output table
KuskoHarvEst:::effort_sensitivity_table(interview_effort_scenarios, flight_data, interview_combos)
```

\clearpage

::: {.small data-latex=""}
_These plots display the times that the trip from each used interview was active and able to be counted via aerial count (vertical lines). Solid black lines indicate the trip would have been counted once, dashed lines indicate the trip would have been counted twice, and dotted lines indicate the trip would have been counted three times. Blue solid lines are trips that could not have been counted. Horizontal grey regions indicate the times the flights were active._
:::

```{r make-plots-interview-data-exclusion, results = "asis", fig.height = 4, fig.width = 7}
junk = lapply(1:nrow(interview_combos), function(i) {
  cat("### Data Source(s):", paste(names(interview_combos)[which(unlist(interview_combos[i,]))], collapse = " & "), "{-}")
  junk = effort_plot(flight_data, interview_effort_scenarios[[i]], FALSE)
})
```

\clearpage
